EGGs are adhesive!

### 2025-03-11 calco/main.tex
cose

\begin{restatable}{lemma}{pbm}\label{lem:pbmono}
	The class $\pbc$ is closed under composition, decomposition and it is stable under pullbacks and pushouts.
\end{restatable}
\begin{proof}
	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability under pushouts is the first point of \Cref{prop:kerset}. We are left with stability under pullbacks.
\end{proof}

@@

We have to show that the top face of the cube with which we have began is a pushout. Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$. Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that	$v_E\circ h'_E=w_E\circ k'_E$ and $v_V\circ h'_V=w_V\circ k'_V$.

\noindent 
\parbox{9cm}{ We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.  Concretely we have to construct the dotted arrow $v_C$ which fits in the diagram aside.} \hfill \parbox{3cm}{
\xymatrix@C=10pt@R=6pt{
	&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
	B_3'  \ar@{>>}[dd]_{q_3'}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>>}[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
	&Q_1'\ar@{>->}[rr]|\hole^(.65){h'_Q} \ar[dl]_{k'_Q} && Q_2' \ar[dl]^(.4){z_Q'}\ar[dr]^{o_Q}\\
	Q'_3 \ar@{>->}[rr]_{p_Q'} & & Q'_4\ar@{.>}[rr]_{v_C} && Q
}}

Now, consider the cube below, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback. We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
\[\xymatrix@C=10pt@R=10pt{
	&B_1'\ar@{>>}[dd]|(.53)\hole^(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rrrr]^{h_V'} \ar[dl]_(.6){k_V'} &&&& B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]^-{k_{x_1}} \ar[dd]_{k_{w}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{u_1}}\\
	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rrrr]^(.7){p_V'} & & &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
	&T\ar@{>->}[rrrr]|(.68)\hole_{x_1} \ar[dl]_{w} &&&& U\ar[dl]^(.4){u_1} && K_{m_3\circ q'_3} \ar@{>->}[rr]_-{k_{y_1}} && K_{q'_4} \\
	Y \ar@{>->}[rrrr]_{y_1} & & && Q'_4}\]

By construction we have that 	$m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1 = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2$ and

Since $m_3$ and $m_2$ are monos we have
\[\begin{split}
	q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2
\end{split}\qquad\begin{split}
	q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2
\end{split}\]
Computing, we obtain
\[\begin{split}
	q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\
	&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\
	&= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
	&= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\
	&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 \\
	&= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\
	&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}
\end{split}\qquad\begin{split}
	q \circ v_V \circ \pi_{q'_4}^1 \circ k_{t_V'} &= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^1 \\
	&= q \circ z_V \circ \pi_{m_2 \circ q_2'}^1 \\
	&= z_C \circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
	&= z_C \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\
	&= q \circ z_V \circ \pi_{m_2 \circ q_2'}^2 \\
	&= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\
	&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{t'_V}
\end{split}\]
Since the previous cube has a pushout as top face, by universal property, we have
\[
q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
\]
hence, $v_C$ is the mediating arrow.
\[
v_C \circ q'_4 \circ \pi_{q'_4}^1 = v_C \circ q'_4 \circ \pi_{q'_4}^2
\]

	\commentato {Now, notice that
	\[s_1 \circ m_1 \circ q_1 = q'_2 \circ h'_V = h'_C \circ q'_1 \quad  	q'_4 \circ z'_V = z'_Q \circ q'_2= u_1\circ m_2 \circ q'_2\]

	\[
\begin{split}
	y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
\end{split}%\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'\end{split}
\]
Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p'_C = y_1 \circ m_3$.}

	By \Cref{prop:reg_epi_coeq}, $d_C$ is the coequalizer of its kernel pair. On the other hand, by \Cref{lemma:pushouts_kernel_pairs}, we know that the top face of the cube below is a pushout.
	\[\begin{tikzcd}[row sep=20, column sep = 20]
		& {K_{s_2\circ m_1 \circ q_1'}} && {K_{m_2\circ q_2'}} \\
		{K_{m_3 \circ q_3'}} && {K_{q_4'}} \\
		& {B'_1} && {B'_2} \\
		{B'_3} && {B'_4}
		\arrow["{k_{h'_V}}", from=1-2, to=1-4]
		\arrow["{k_{k_V'}}"', from=1-2, to=2-1]
		\arrow["{\pi_{s_2\circ m_1 \circ q_1'}^1}"'{pos=0.7}, from=1-2, to=3-2]
		\arrow["{k_{t_V'}}", from=1-4, to=2-3]
		\arrow["{\pi_{m_2\circ q_2'}^1}", from=1-4, to=3-4]
		\arrow["{k_{p_V'}}"{pos=0.8}, from=2-1, to=2-3, crossing over]
		\arrow["{\pi_{m_3 \circ q_3'}^1}"', from=2-1, to=4-1]
		\arrow["{h_V'}"{pos=0.7}, from=3-2, to=3-4]
		\arrow["{\pi_{q_4'}^1}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
		\arrow["{k_V'}"', from=3-2, to=4-1]
		\arrow["{t_V'}", from=3-4, to=4-3]
		\arrow["{p_V'}"', from=4-1, to=4-3]
	\end{tikzcd}\]
	And, since $m_3$ and $m_2$ are monos,
	\[\begin{split}
		q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2
	\end{split}\qquad\begin{split}
		q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2
	\end{split}\]

	Computing, we obtain
	\[\begin{split}
		q \circ \phi \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'} \\ &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{p'_V}
	\end{split}\qquad\begin{split}
		q \circ \phi \circ \pi_{q'_4}^1 \circ k_{t_V'} &= q \circ \phi \circ t_V' \circ \pi_{m_2 \circ q_2'}^1 \\ &= q \circ z_V \circ \pi_{m_2 \circ q_2'}^1 \\ &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\ &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\ &= q \circ z_V \circ \pi_{m_2 \circ q_2'} \\ &= q \circ \phi \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{t'_V}
	\end{split}\]

	Since the previous cube has a pushout as top face, by universal property, we have
	\[
	q \circ \phi \circ \pi_{q'_4}^1 = q \circ \phi \circ \pi_{q'_4}^2
	\]
	hence, $v$ is the mediating arrow.
	\[
	v \circ q'_4 \circ \pi_{q'_4}^1 = v \circ q'_4 \circ \pi_{q'_4}^2
	\]

>>>>

\begin{restatable}{lemma}{pbm}\label{lem:pbmono}
	The class $\pbc$ is closed under composition, decomposition and it is stable under pullbacks and pushouts.
\end{restatable}
\begin{proof}
	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability under pushouts is the first point of \Cref{prop:kerset}. We are left with stability under pullbacks. Consider the diagrams below, in which the first square is a pullback with $h$ in $\pbc$. In particular, by \Cref{prop:eqhyp_complete}, the two halves of the diagram on the right are pullbacks and so, by \Cref{lem:pb1} the whole rectangle is a pullback too.

	\[\]

		\[
	\xymatrix@C=10pt@R=10pt{&& & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'}  \\\mathcal{P} & & \mathcal{G}_1 &
	A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
	&& V_{\mathcal{P}} && V_1 && Q_1\\
	 &&&&A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E}  \\
		\mathcal{G}_2 && \mathcal{G}_3 & V_3 \ar@{>->}[rr]_{p_E} & & A_4 && V_2 && V_3 && Q_3 }
	\]

	Thus, by \Cref{lem:pb1} also the right rectangle is a pullback.
\end{proof}

@@

We have to show that the top face of the cube with which we have began is a pushout. Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$. Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
\[v_E\circ p'_E=w_E \quad v_V\circ p'_V=w_V \quad v_E\circ z'_E=o_e \quad v_V\circ z'_V=o_V\]

\commentato{\xymatrix@C=10pt@R=6pt{
		&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
		B_3'  \ar@{>>}[dd]_{q_3'}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>>}[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
		&Q_1'\ar@{>->}[rr]|\hole^(.65){h'_Q} \ar[dl]_{k'_Q} && Q_2' \ar[dl]^(.4){z_Q'}\ar[dr]^{o_Q}\\
		Q'_3 \ar@{>->}[rr]_{p_Q'} & & Q'_4\ar@{.>}[rr]_{v_C} && Q
}}

We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.

Now, consider the cube below, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback. We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
\[\xymatrix@C=10pt@R=10pt{
	&B_1'\ar@{>>}[dd]|(.53)\hole^(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rrrr]^{h_V'} \ar[dl]_(.6){k_V'} &&&& B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]^-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\
	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rrrr]^(.7){p_V'} & & &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
	&T\ar@{>->}[rrrr]|(.68)\hole_{x_1} \ar[dl]_{w} &&&& U\ar[dl]^(.4){u_1} && K_{m_3\circ q'_3} \ar@{>->}[rr]_-{k_{p'_V}} && K_{q'_4} \\
	Y \ar@{>->}[rrrr]_{y_1} & & && Q'_4}\]

By construction we have that 
\[m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1 = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad  m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 = m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2 \]
but since $m_3$ and $m_2$ are monos this implies
\[q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2\]

Computing, we obtain
\[\begin{split}
	q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\
	&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\
	&= w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
	&= w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\
	&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 \\
	&= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\
	&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}
\end{split}\qquad\begin{split}
	q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} &= q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 \\
	&= q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 \\
	&= o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
	&= o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\
	&= q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 \\
	&= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\
	&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
\end{split}\]
Since the previous cube has a pushout as top face, by universal property, we have
\[
q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
\]

Now, $q'_4$ is a regular epi and so it is the coequalizer of its kernel pair, hence there exists $v_Q\colon Q'_4\to Q$ such that $v_Q\circ q'_4=q\circ v_V$ and we can conclude.
\end{proof}
